Simulation Study: AdaPT with null model option (step covariate)

### 2018-10-31 datasets/simulations/simulations-informative-cubic.Rmd
Update text at top of some simulation Rmds

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (cubic) function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

>>>>

In this set of simulations, we consider settings with both null and non-null
tests with an informative and uninformative covariate. The informative covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (cubic) function of the covariate. The uninformative covariate is simply
uninformly sampled independently from the interval [0, 1]. The uninformative covariate is included
as a baseline to compare the informative covariate against. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

### 2018-10-31 datasets/simulations/simulations-informative-sine.Rmd
Update text at top of some simulation Rmds

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (sine) function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

>>>>

In this set of simulations, we consider settings with both null and non-null
tests with an informative and uninformative covariate. The informative covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (sine) function of the covariate. The uninformative covariate is simply
uninformly sampled independently from the interval [0, 1]. The uninformative covariate is included
as a baseline to compare the informative covariate against. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

### 2018-10-31 datasets/simulations/simulations-informative-step.Rmd
Update text at top of some simulation Rmds

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a non-smooth (monotone) step function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

>>>>

In this set of simulations, we consider settings with both null and non-null
tests with an informative and uninformative covariate. The informative covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a non-smooth monotone step function of the covariate. The uninformative covariate is simply
uninformly sampled independently from the interval [0, 1]. The uninformative covariate is included
as a baseline to compare the informative covariate against. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

### 2018-10-31 datasets/simulations/simulations-uasettings.Rmd
Add/modify descriptions of UA setting Rmds; add UA sims w more non-null
Update text at top of some simulation Rmds

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-cubic.Rmd`.

>>>>

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. Both informative and uninformative covariates are included in the setting as described in
`simulations-informative-cubic.Rmd`. The effect sizes for non-null tests are
sampled from unimodal distributions composed of a mixture of normal distributions,
as described in the original adaptive shrinkage (ASH) manuscript (Stephens, 2016).

### 2018-10-31 datasets/simulations/supplementary/simulations-informative-step-nullAdaPT.Rmd
Fix relative path of R directory for suppl Rmds; change ua output file names
Update text at top of some simulation Rmds

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a non-smooth (monotone) step function of the covariate. We include simulation
results again with Gaussian, t-distributed, and Chi-Squared distributed test statistics.

>>>>

In this set of simulations, we consider settings with both null and non-null
tests with informative and non-informative covariates as described in
`simulations-informative-step.Rmd`.
